### 2014-10-19 thesis/method/classification.tex
Wrote introduction to classification and moved stuff to evaluation #12

\chapter{Classification and Supervised Learning Algorithms}
  \label{chap:classification}

\section{Model construction}
Here we present the various classification schemes we used in order to find
the best model for the trauma LOS data.

\subsection{Single classifier}
First we sought to compare the suitability and performance of various
classifiers by themselves (later we looked at \textit{ensembles} of
classifiers, when more than one is involved in making a prediction).
These are the
classifiers studied: \todo{expand a bit more here, maybe list the
configuration parameters}
\begin{itemize}
  \item Na\"{i}ve Bayes
  \item Decision tree (C4.5)
  \item Logistic regression
  \item Support vector machine
  \item $K$-nearest neighbour
  \item Feed-forward neural network (multilayer perceptron)
\end{itemize}

Each classifier was trained using ten-fold cross-validation for each of the
7 data sets obtained from the various feature selection methods described
above. This was repeated 30 times for each classifier and the reasons for
this, as well as the metrics used to assess the performance of these
classifiers, are described in Section \ref{sec:perfeval} of this chapter.

In addition to the feature selection methods, we also used the WEKA 3.7.11
\citep{Hall2009} implementation of the above classifiers for our experiments.
Training was automated using a Bash shell script (whose source can be found
in the appendix) that programmatically read in a list of classifiers to
train and repeated the procedure any specified number of times, writing the
results to a specified directory for later reference.

\subsubsection{Parameter tuning}
It is difficult in data mining to apply an algorithm out-of-the-box and have
it perform optimally on a given data set \citep{Witten2005}. Therefore, time
must be spent tweaking and tuning the parameters of a classifier in order to
improve classification performance. This was the next step we took. We
considered a range of values for various parameters of each classification
scheme, and tried some of these new configurations by hand and some by using
WEKA's cross-validation parameter selection class. The configurations tested,
as well as how they were executed, are listed in this table:
\todo{insert table!}

\subsection{Ensemble classifiers}
In order to improve upon the performance of individual classifiers, we also
tested the performance of ensembles of classifiers -- that is, combining the
predictions of several different classifiers, or several of the same
classifier. Specifically, the ensemble methods used were:
\begin{itemize}
  \item Random Forests
  \item Bagging
  \item Stacked generalisation (stacking)
  \item Boosting (AdaBoostM1)
\end{itemize}

Again, we were able to create predictive models using the implementations of
these ensemble methods in WEKA 3.7.11. Since ensemble classifiers are not
actual classifiers but a way to train and combine the predictive power of more
than one classifier, we list the combinations of classifiers used in our
ensemble methods:
\todo{insert table!}

>>>>

\chapter{LOS Classification and Supervised Learning}
  \label{chap:classification}

In order to use a supervised learning algorithm to identify objects with
a particular classification, we first need \textit{feature vectors} to
describe these objects. In our case, each patient is converted into one
feature vector, where each \textit{feature} in this vector tells us
something about the
patient that can help us decide which LOS category he or she should be
placed in. The features comprising each feature vector must be the same,
but with different values. By comparing feature values between different
vectors, we are able to decide which \textit{class} or category a patient
belongs in. For example, if we wanted to classify the weather on a given
day as ``good'' or ``bad'', we could use two features -- temperature and
the amount of rain -- which are likely to be key indicators. Classifying
several days simply involves creating a feature vector that corresponds
to each day, with differing values for the temperature and the amount of
rain, and using these values to decide whether or not a day had good or
bad weather.

Since we will be using supervised learning techniques, we need
\textit{training examples}, which consist of a set of feature vectors
that are already labelled with the class that it belongs in. These
training examples are then used by a classifier to ``learn'' the
relationship linking the feature vectors to their class labels. In this
chapter we describe each of the learning algorithms we used to model the
relationship between the feature vectors and the LOS.

\section{ZeroR and OneR}

\section{Na\"{i}ve Bayes}

\section{Decision Tree (C4.5)}

\section{Logistic Regression}

\section{Support Vector Machine (SVM)}

\section{$k$-Nearest Neighbour}
\subsection{Basic Algorithm}

\subsection{Extensions}
\subsubsection{K*: an Entropy-Based Distance Function}

\subsubsection{Ranked Distance}

\section{Feed-forward Neural Network}

### 2014-10-19 thesis/method/evaluation.tex
Wrote introduction to classification and moved stuff to evaluation #12

>>>>

\subsection{Single classifier}
First we sought to compare the suitability and performance of various
classifiers by themselves (later we looked at \textit{ensembles} of
classifiers, when more than one is involved in making a prediction).
These are the
classifiers studied: \todo{expand a bit more here, maybe list the
configuration parameters}
\begin{itemize}
  \item Na\"{i}ve Bayes
  \item Decision tree (C4.5)
  \item Logistic regression
  \item Support vector machine
  \item $K$-nearest neighbour
  \item Feed-forward neural network (multilayer perceptron)
\end{itemize}

Each classifier was trained using ten-fold cross-validation for each of the
7 data sets obtained from the various feature selection methods described
above. This was repeated 30 times for each classifier and the reasons for
this, as well as the metrics used to assess the performance of these
classifiers, are described in Section \ref{sec:perfeval} of this chapter.

In addition to the feature selection methods, we also used the WEKA 3.7.11
\citep{Hall2009} implementation of the above classifiers for our experiments.
Training was automated using a Bash shell script (whose source can be found
in the appendix) that programmatically read in a list of classifiers to
train and repeated the procedure any specified number of times, writing the
results to a specified directory for later reference.

\subsubsection{Parameter tuning}
It is difficult in data mining to apply an algorithm out-of-the-box and have
it perform optimally on a given data set \citep{Witten2005}. Therefore, time
must be spent tweaking and tuning the parameters of a classifier in order to
improve classification performance. This was the next step we took. We
considered a range of values for various parameters of each classification
scheme, and tried some of these new configurations by hand and some by using
WEKA's cross-validation parameter selection class. The configurations tested,
as well as how they were executed, are listed in this table:
\todo{insert table!}

\subsection{Ensemble classifiers}
In order to improve upon the performance of individual classifiers, we also
tested the performance of ensembles of classifiers -- that is, combining the
predictions of several different classifiers, or several of the same
classifier. Specifically, the ensemble methods used were:
\begin{itemize}
  \item Random Forests
  \item Bagging
  \item Stacked generalisation (stacking)
  \item Boosting (AdaBoostM1)
\end{itemize}

Again, we were able to create predictive models using the implementations of
these ensemble methods in WEKA 3.7.11. Since ensemble classifiers are not
actual classifiers but a way to train and combine the predictive power of more
than one classifier, we list the combinations of classifiers used in our
ensemble methods:
\todo{insert table!}
